---
title: Reproduced Analysis of FARS data
author: 
date: 
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(knitr)
library(ggthemes)
load("/Users/Chloe/Project_1/data/clean_fars.RData")
source("/Users/Chloe/Project_1/R/fars_functions.R")
```


## Results

**Percentages of drivers testing positive by drug type, sex, and year group**

```{r}
knitr::kable(table_1, col.names = c("Drug type", "F 1999-2002",
                             "F 2003-2006", "F 2007-2010",
                             "M 1999-2002", "M 2003-2006",
                             "M 2007-2010"))
```

**Figure 1: Prevalence of nonalcoholic drugs in fatally injured drivers by year and age group**

```{r fig.width = 8, fig.height = 5}
graph_1_fars
# code for graph in function script
```

**Figure 2: Prevalence of nonalcoholic drugs in fatally injured drivers by year and drug type** 

```{r fig.width=8, fig.height = 5}
graph_2_fars
# code for graph in function script
```

**Figure 3: Prevalence of nonalcoholic drugs in fatally injured drivers by year and age group**

```{r fig.width = 8, fig.height = 5}
graph_3_fars
# code for graph in function script
```

**Prevalence of drugs in fatally injured drivers for 1999 and 2010 by drug type**

```{r}
knitr::kable(table2, col.names = c("Drug Type", "1999", "2010"))
```

**Statistics for testing for trend in prevalence of drugs over study years by drug type using Cochran-Armitage trend test**

```{r}
knitr::kable(drug_trend_tests_ca)
```

**Statistics for testing for trend in prevalence of drugs over study years by drug type using Wald test of logistic regression coefficient for 'year'**

```{r}
knitr::kable(drug_trend_tests_log_reg)
```


